\textbf{Development of outdoor air pollution models for estimating exposure in the Barcelona Life Study Cohort (BiSC)}

### 2024-01-03 manuscript_BiSC_outdoor_AP.tex
Updates from Overleaf

\textbf{\Cref{fig2}} presents the distribution of the observed and estimated NO\textsubscript{2}, PM\textsubscript{2.5} and BC concentrations from the LUR, DM, and HM. The data shown are long-term estimated concentrations of pollutants, after averaging weekly estimates for all the study period (2019 - 2021).

>>>>

\textbf{\Cref{fig2}} presents the distribution of the observed and estimated NO\textsubscript{2}, PM\textsubscript{2.5}, BC,  PM\textsubscript{2.5 - Fe}, PM\textsubscript{2.5 - Cu}, and PM\textsubscript{2.5 - Zn} concentrations from the LUR, DM, and HM. The data shown are long-term estimated concentrations of pollutants during the entire pregnancy period, after averaging weekly estimates for all the study period (2019 - 2021).
